### 2014-10-29 doc/thesis/evaluation.tex
Minor improvements to the text about typing MD5 library

The MD5 library \citep{lmd5} is the case study that we used to
introduce Typed Lua's description files.
We chose this case study because it is simple and contains just
one module, being a good example for introducing how we can use
Typed Lua's description files for giving a statically typed
interface to a Lua library that is written in C, and to 
introduce how we can type an \emph{userdata}.
Table \ref{tab:evalmd5} sumarizes the evaluation results for MD5.

@@

This case study shows that type annotations are a good source of documentation,
tough it might be not so obious to identify which functions discard extra
parameters when we are typing an external library.
Reading the source code and the library's test script was essential to confirm
the typing of \texttt{update}.

@@

>>>>

We chose the MD5 library \citep{lmd5} as a case study because it is
simple and contains just one module.
We needed a simple case study to introduce Typed Lua's description
files and \texttt{userdata} declarations.
These Typed Lua's mechanims allow programmers to give statically typed
interfaces to Lua libraries that are written in C.
Table \ref{tab:evalmd5} sumarizes the evaluation results for MD5.

@@

This case study shows that it might be not so obvious to identify which
functions discard extra arguments when we are typing an external library.
In this case study, reading its source code and test script was essential
to confirm the typing of \texttt{update}.

@@

\begin{itemize}
\item Tidal Lock
\item Typed Clojure
\item Gradual Python
\item Gradualtalk
\item Typed Racket
\item Dart
\item TypeScript
\end{itemize}
